\documentclass{ctuthesis}
\ctusetup{
xdoctype = M,
xfaculty = F3,
mainlanguage = english,
titlelanguage = english,
title-english = {Part localization for robotic manipulation},
title-czech = {},
department-english = {},
author = {C\'esar Sinchiguano},
supervisor = {Dr Gaël Pierre Écorchard.},
supervisor-address = {Czech Institute of Informatics, Robotics, and Cybernetics,
Office B-323,Jugoslávských partyzánů 3,
160 00  Prague 6},
month = 5,
year = 2019,
keywords-czech = {Detekce objektů, Odhad Pozice, Robotika, Bodová Data},
keywords-english = {Object Detection, Pose Estimation, Robotics, Point Cloud Data},
pkg-hyperref=true
}
\ctusetup{ pkg-amsthm = false }
\ctuprocess

% Acknowledgements
\begin{thanks}
I would like to express my sincere gratitude to .....
\end{thanks}

% Declaration
\begin{declaration}
I hereby declare that the presented work was developed independently and that I have listed
all sources of information used within it in accordance with methodical instructions for
observing the ethical principles in the preparation of university theses.
Prague, \ctufield{day}.~\monthinlanguage{title}~\ctufield{year}

\end{declaration}

\begin{abstract-english}

The new generation of the collaborative robots allows the use of small robot arms working with human workers, e.g. the YuMi robot, a dual 7-DOF robot arms designed for precise manipulation of small objects. For the further acceptance of such a robot in the industry, some methods and sensors systems have to be developed to allow them to perform a task such as grasping a specific object. If the robot wants to grasp an object, it has to localize the object relative to itself. This is a task of object recognition in computer vision, the art of localizing predefined objects in image sensor data. 
This master thesis presents a pipeline for object recognition of a single isolated model in point cloud. The system uses point cloud data rendered from a 3D CAD model and describes its characteristics using local feature descriptors. These are then matched with the descriptors of the point cloud data from the scene to find the 6-DoF pose of the model in the robot coordinate frame. This initial pose estimation is then refined by a registration method such as ICP. A robot-camera calibration is performed also.
The contributions of this thesis are as follows: The system uses FPFH (Fast Point Feature Histogram) for describing the local region and a hypothesize-and-test paradigm, e.g. RANSAC in the matching process. In contrast to several approaches those whose rely on Point Pair Features as feature descriptors and a geometry hashing, e.g. voting-scheme as the matching process.
\end{abstract-english}


\begin{abstract-czech}
Nová generace spolupracujících robotů umožňuje použití malých robotických ramen pracujících s lidskými pracovníky, např. robota YuMi, dvojitá robotická ramena 7-DOF určená pro přesnou manipulaci s malými předměty. Pro další přijetí takového robota v průmyslu musí být vyvinuty některé metody a systémy senzorů, které jim umožní provádět úkol, například uchopení určitého objektu. Pokud chce robot uchopit objekt, musí objekt umístit relativně vůči sobě. To je úkol rozpoznávání objektů v počítačovém vidění, což je umění lokalizace předdefinovaných objektů v datech obrazového snímače.
Tato diplomová práce představuje potrubí pro rozpoznávání objektů jednoho izolovaného modelu v bodovém mračnu. Systém využívá data z bodového mračna vykreslená z 3D CAD modelu a popisuje jeho charakteristiky pomocí lokálních deskriptorů funkcí. Ty jsou pak porovnány s deskriptory dat z bodového mračna ze scény, aby se 6-DoF pozice modelu v souřadném rámci robota. Tento počáteční odhad pozice je pak vylepšen metodou registrace, jako je ICP. Provádí se také kalibrace robotické kamery.
Příspěvky této práce jsou následující: Systém používá FPFH (Fast Point Feature Histogram) pro popis lokální oblasti a hypotézu - a paradigma testu, např. RANSAC v procesu párování. Na rozdíl od několika přístupů k těm, které se spoléhají na vlastnosti Point Pair jako deskriptory vlastností a geometrické hašování, např. hlasovací systém jako proces shody.
\end{abstract-czech}


%##########################
%Default package loading
\usepackage{import}
%\usepackage{biblatex}
%\addbibresource{mybib.bib}
%for graphics
\usepackage{graphicx}
\usepackage{subfig}
%\usepackage[options ]{algorithm2e}
\usepackage[]{algorithm2e}
%for algorithm

%for appendix 
\usepackage{tabularx, array, booktabs}

%adding reference from an external file
\usepackage{xr}


%//////////////_START BODY_////////////////////////
\begin{document}
\maketitle


% Introduction-->>Chapter one
\import{01_Introduction/}{Intro1.tex}

% Introduction-->>Chapter two
\import{02_RelatedWork/}{RelatedWork2.tex}

% Background-->>Chapter three
\import{03_Background/}{Background3.tex}


% Theory-->>Chapter four
\import{04_CamRob/}{CamRob4.tex}


% Theory-->>Chapter five
\import{05_PoseObject/}{PoseObject5.tex}


% Theory-->>Chapter six
\import{06_Results/}{Results6.tex}


% Theory-->>Chapter seven
\import{07_FutureWork/}{FutureWork7.tex}

% Theory-->>Chapter eight
\import{08_Conclusions/}{Conclusions8.tex}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\import{ZReferences/}{reference.tex}
\import{ZAppendixA/}{AppendixA.tex}

\end{document}
%//////////////_END BODY_////////////////////////

